---
title: "Differences Between Columns Of A Tibble"
output:
  html_document:
    df_print: paged
---


## Disclaimer
This notebook summarizes experiments on finding differences between columns of a tibble.


## Experiments
In a first step, we are looking at the result of `all_equal()`.

When trying to find the differences, it might be beneficial to do joins between the columns of interest.


## Example Dataset
The following data set is used as an example to show a few results from our experiments.

```{r}
tbl_rc <- tibble::tibble(Tier = c("CH 120.0976.8774.7",
                                  "CH 120.0976.8775.2",
                                  "CH 120.0976.8776.6",
                                  "CH 120.0976.8777.0"),
                         RCAlt = c("07",
                                   "INC",
                                   "INC",
                                   "INC"),
                         RCNeu = c("07",
                                   "INC",
                                   "KR",
                                   "INC"),
                         Nako = c(0,0,1,0))
tbl_rc
```


## Equality
Can we use `all.equal()` to get a comparison between the column `RCAlt` and `RCNeu`. A first idea is to split the existing tibble `tbl_rc` into two tibbles

```{r}
library(dplyr)
tbl_rc_alt <- tbl_rc %>% select(Tier, RCAlt, Nako) %>% mutate(BreedCode = RCAlt) %>% select(Tier, BreedCode, Nako)
tbl_rc_neu <- tbl_rc %>% select(Tier, RCNeu, Nako) %>% mutate(BreedCode = RCNeu) %>% select(Tier, BreedCode, Nako)
```

We are using `tbl_rc_alt` and `tbl_rc_neu` as arguments for `all_equal()`.

```{r}
dplyr::all_equal(tbl_rc_alt, tbl_rc_neu)
```

This result of `all_equal()` is a string telling us on which row the difference between the tibbles occured. With that information we can inspect both tibbles and see the difference. 

```{r}
tbl_rc_alt[3,]
```

```{r}

tbl_rc_neu[3,]
```

But the result of `all_equal()` is rather difficult to be used for further computations.


## Joins
Find the differences with joins

```{r}
dplyr::anti_join(tbl_rc_alt, tbl_rc_neu, by = c("Tier" = "Tier", "BreedCode" = "BreedCode"))
```


```{r, echo=FALSE, results='asis'}
cat(rmddochelper::get_latest_change(), "\n")
```

