---
title: "Differences Between Columns Of A Tibble"
output: html_notebook
---


## Disclaimer
This notebook summarizes experiments on finding differences between columns of a tibble.


## Experiments
In a first step, we are looking at the result of `all_equal()`.

When trying to find the differences, it might be beneficial to do joins between the columns of interest.


## Example Dataset
The following data set is used as an example to show a few results from our experiments.

```{r}
tbl_rc <- tibble::tibble(Tier = c("CH 120.0976.8774.7",
                                  "CH 120.0976.8775.2",
                                  "CH 120.0976.8776.6",
                                  "CH 120.0976.8777.0"),
                         RCAlt = c("07",
                                   "INC",
                                   "INC",
                                   "INC"),
                         RCNeu = c("07",
                                   "INC",
                                   "KR",
                                   "INC"),
                         Nak0 = c(0,0,1,0))
tbl_rc
```


## Joins
Find the differences with joins

```{r}
library(dplyr)
tbl_rc_alt <- tbl_rc %>% select(Tier, RCAlt)
tbl_rc_neu <- tbl_rc %>% select(Tier, RCNeu)
dplyr::anti_join(tbl_rc_alt, tbl_rc_neu, by = c("Tier" = "Tier", "RCAlt" = "RCNeu"))
```


```{r, echo=FALSE, results='asis'}
rmddochelper::get_latest_change()
```

